Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Apply terminology

If we have examples/properties that does not fit into the user documentation, but
would rather be part of a design document, we use \hspec{}.

\hspec{} provides an EDSL for defining specs.  A spec organizes behavior in a
tree structure, and it is defined with \texttt{it} and \texttt{describe}.

>>>>

If we have evidence that does not fit into the user documentation, but would
rather be part of a design document, we use \hspec{}.

\hspec{} provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure, and it is defined with \texttt{it} and \texttt{describe}.
